Dysregulation of Cerebral Hemoglobin Content in Malawian Children with Malaria

### 2021-07-21 figures.Rmd
updated model with up-sample

@@

# recipe
hbox_rec <- recipe(Status ~ ., data = df_hbox_model) %>% 
  step_BoxCox(all_predictors()) %>% 
  step_nzv(all_predictors())

@@

final_res_conf_mat %>% 
  group_by(Truth) %>% 
  summarise(total_true = sum(Freq)) %>% 
  right_join(final_res_conf_mat) %>% 
  mutate(`Percent occurence` = round(Freq/total_true*100, 2)) %>%

  # plot
  ggplot(aes(x = Truth, y = Prediction, fill = `Percent occurence`, label = `Percent occurence`)) +
  geom_tile() +
  geom_text(size = 6) +
  scale_fill_gradient2(low = "#4575b4", high = "#d73027") +

>>>>

library(themis)

@@

# recipe
hbox_rec <- recipe(Status ~ ., data = df_hbox_model) %>% 
  step_BoxCox(all_predictors()) %>% 
  step_nzv(all_predictors()) %>% 
  step_smote(Status) # upsample to deal with unbalanced sample sizes

@@

total_true_UM <- final_res_conf_mat %>% dplyr::filter(Truth == "UM") %>% .$Freq %>% sum()
total_true_CM <- final_res_conf_mat %>% dplyr::filter(Truth == "CM") %>% .$Freq %>% sum()

final_res_conf_mat %>% 
  mutate(total_true = ifelse(Truth == "CM", Freq/total_true_CM, Freq/total_true_UM)) %>% 
  mutate(`Percent occurrence` = round(total_true*100, 2)) %>%

  # plot
  ggplot(aes(x = Truth, y = Prediction, fill = `Percent occurrence`, label = `Percent occurrence`)) +
  geom_tile() +
  geom_text(size = 6) +
  scale_fill_gradient2(low = "#4575b4", high = "#d73027") +
